KV Analysis for Performing-Articulation performances

### 2021-02-01 material/expstimuli/analysis/expression/stim_a/duration.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of performing performance (Duration) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_duration_leg <- duration[Subcomponent == "Legato" & Mean < duration_all[Subcomponent == "Legato"]$Mean+3*duration_all[Subcomponent == "Legato"]$SD & Mean > duration_all[Subcomponent == "Legato"]$Mean-3*duration_all$SD]
print(excluded_duration_leg)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Legato"]$N-nrow(excluded_duration_leg)`

@@

<!-- # Duration Variability -->
<!-- ```{r cv, echo = FALSE} -->
<!-- # for each participant -->
<!-- cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)] -->
<!-- print(cv) -->
<!-- ``` -->

<!-- ```{r cv_box, echo = FALSE} -->
<!-- p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) + -->
<!--   geom_boxplot() + -->
<!--   geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) -->
<!-- p_cv_box -->
<!-- ``` -->

<!-- ### Exclude outlier performacnes -->
<!-- ```{r cv_outlier, echo = FALSE} -->
<!-- # for all -->
<!-- cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))] -->
<!-- print(cv_all) -->

<!-- excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD] -->
<!-- print(excluded_cv) -->
<!-- ``` -->

>>>>

***Duration values from this analysis were used.***

Description: This is a rough overview of performing performance (Duration) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Performing-Articulation performances: data from the performing condition (articulation)

@@

# Valid performances (exclude Duration outliers)
- Exclude mean Duration outside 3SD
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_duration_leg <- duration[Subcomponent == "Legato" & Mean < duration_all[Subcomponent == "Legato"]$Mean+3*duration_all[Subcomponent == "Legato"]$SD & Mean > duration_all[Subcomponent == "Legato"]$Mean-3*duration_all$SD]
print(excluded_duration_leg)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Legato"]$N-nrow(excluded_duration_leg)`

@@

### 2021-02-01 material/expstimuli/analysis/expression/stim_a/ioi_onset.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of performing performance (IOI-Onset) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

@@

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

>>>>

Description: This is a rough overview of performing performance (IOI-Onset) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Performing-Articulation performances: data from the performing condition (articulation)

@@

@@

### 2021-02-01 material/expstimuli/analysis/expression/stim_a/kv.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of performing performance (KV) from teaching-v2.0.

@@

```{r velocity, include = FALSE}
# # convert bpm to ms
# dt_kv[Tempo == 120]$Tempo <- 250
# dt_kv[Tempo == 110]$Tempo <- 273
# dt_kv[Tempo == 100]$Tempo <- 300

# define subcomponents
# for intervals
ls_legato <- list(c(1:4), c(9:16), c(21:24), c(40:46))
ls_staccato <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))
ls_forte <- list(c(1:4), c(9:16), c(21:24), c(40:46))
ls_piano <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))

@@

### Valid performances (exclude outliers)
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_kv_leg <- kv[Subcomponent == "Legato" & Mean < kv_all[Subcomponent == "Legato"]$Mean+3*kv_all[Subcomponent == "Legato"]$SD & Mean > kv_all[Subcomponent == "Legato"]$Mean-3*kv_all$SD]
print(excluded_kv_leg)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Legato"]$N-nrow(excluded_kv_leg)`

#### Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
excluded_kv_sta <- kv[Subcomponent == "Staccato" & Mean < kv_all[Subcomponent == "Staccato"]$Mean+3*kv_all[Subcomponent == "Staccato"]$SD & Mean > kv_all[Subcomponent == "Staccato"]$Mean-3*kv_all$SD]
print(excluded_kv_sta)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Staccato"]$N-nrow(excluded_kv_sta)`

<!-- ```{r export, include = FALSE} -->
<!-- kv_valid <- dt_kv[, .(N = length(Velocity), Mean = mean(Velocity)), .(SubNr, TrialNr)] -->
<!-- fwrite(kv_valid, "./kv_valid.csv") -->
<!-- ``` -->

<!-- # KV Variability -->
<!-- ```{r cv, echo = FALSE} -->
<!-- # for each participant -->
<!-- cv <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), CV = sd(Velocity)/mean(Velocity)) , by = .(SubNr, TrialNr)] -->
<!-- cv -->
<!-- ``` -->

<!-- ```{r cv_box, echo = FALSE} -->
<!-- p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) + -->
<!--   geom_boxplot() + -->
<!--   geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) -->
<!-- p_cv_box -->
<!-- ``` -->

<!-- ### Exclude outlier performances -->
<!-- ```{r cv_outlier, echo = FALSE} -->
<!-- # for all -->
<!-- cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))] -->
<!-- print(cv_all) -->

<!-- excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD] -->
<!-- print(excluded_cv) -->
<!-- ``` -->

>>>>

Description: This is a rough overview of performing performance (KV) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Performing-Articulation performances: data from the performing condition (articulation)

@@

```{r velocity, include = FALSE}
# define subcomponents
# for intervals
ls_legato <- list(c(1:4), c(9:16), c(21:24), c(40:46))
ls_staccato <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))
ls_forte <- list(c(1:4), c(9:16), c(21:24), c(40:46))
ls_piano <- list(c(6:7), c(18:19), c(29:31), c(36:38), c(48:50), c(53:55), c(58:64))

@@
